Contracts for unions and intersections are hard for Nickel

### 2021-05-26 paper.tex
Reading sections 3–5

In statically typed languages, and more specifically in functional programming
languages, sums (also called tagged unions, or discriminated unions) are usually
preferred, as constructors for algebraic datatypes. \unsure{This is a very
    misleading statement at best. Sums are "tagged union" sure, but that refers
to an encoding a sums with unions, certainly not an encoding of unions with
sums!} [references]. Sums are unions' cousin where the alternatives are
syntactically separated by an associated discriminating label. Well-known
programming languages with first-class tagged unions include Haskell, OCaml,
Rust, Scala, PureScript, Elm, Swift and many more.

@@

Having a witness of size 1 for every contract failure is a nice to have property
since it means, for example, that every time that a contract is violated,
the stack trace is enough to understand how it was violated, and to potentially
come up with a minimal example that breaks the contract.
However, when unions get introduced, it is lost.
Consider now the program presented at Figure \ref{fig:wrong-union-function},
this program (and in particular, \nickel{f}'s contract) still presents a problem,
since \nickel{fun x => x - 7} does not map positive numbers to positive numbers,
nor does it map positive numbers to non-positive numbers, so it won't be a valid
value for the union of those contracts.

@@

Starting with the Keil and Thiemann work \cite{KeilThiemannUnionIntersection},
they noticed that, since union contracts should share information between
different application contexts, while intersection contracts should behave
independently between each application context, the system becomes much
simpler if every contract gets transformed into a union of intersections
of other contracts, by using the usual De Morgan laws,
and then eagerly opening up unions, but postponing intersection
contracts as much as possible.
\todo{This assumes the difficulty has been previously explained}

For instance, if the value \nickel{V} is wrapped with contract
\todo{(Yann) Contracted means
something else I think.
(Teo) changed}
\nickel{A & (B | C)}, then, before the contract is checked,
it will get opened up to something equivalent to
\nickel{(A & B) | (A & C)}.

This straightforward solutions makes composing the Keil and Thiemann
system with other existing systems more difficult; in the words
of Williams, Morris, and Wadler:
"(\ldots) the monitoring semantics for contracts of intersection and union types given by Keil
and Thiemann are not uniform. (\ldots) If uniformity helps composition, then
special cases can hinder composition."\cite{RootCauseOfBlame}
\info{(Yann) Does
it also make it less efficient? If $(A \& B)$ fails because of $B$, their
development causes to recheck the contract $A$ that has been duplicated?}
And it also could harm performance, or at least complicate an implementation,
since some sharing mechanism should be used to avoid checking the same contract,
over the same value, multiple times.

@@

@@

>>>>

In statically typed languages, and more specifically in functional programming
languages, sums (also called tagged unions, or discriminated unions) are usually
preferred, as constructors for algebraic datatypes. [references]. Sums are unions' cousin where the alternatives are
syntactically separated by an associated discriminating label. Well-known
programming languages with first-class tagged unions include Haskell, OCaml,
Rust, Scala, PureScript, Elm, Swift and many more.

@@

Having a witness of size 1 for every contract failure is a nice to have property
since it means, for example, that every time that a contract is violated,
the stack trace is enough to understand how it was violated, and to potentially
come up with a minimal example that breaks the contract.
However, when unions get introduced, it is lost.
Consider now the program presented in Figure \ref{fig:wrong-union-function},
this program (and in particular, \nickel{f}'s contract) still presents a problem,
since \nickel{fun x => x - 7} does not map positive numbers to positive numbers,
nor does it map positive numbers to non-positive numbers, so it won't be a valid
value for the union of those contracts.

@@

\subsection{Keil and Thiemann}
\label{sec:keil-thiemann}
\unsure{Subsection title?}
Starting with the Keil and Thiemann work \cite{KeilThiemannUnionIntersection},
they noticed that, since union contracts should share information between
different application contexts, while intersection contracts should behave
independently between each application context, the system becomes much
simpler if every contract gets transformed into a union of intersections
of other contracts, by using the usual De Morgan laws,
and then eagerly opening up unions, but postponing intersection
contracts as much as possible.
\todo{This assumes the difficulty has been previously explained}

For instance, if the value \nickel{V} is wrapped with contract
\nickel{A & (B | C)}, then, before the contract is checked,
it will get opened up to something equivalent to
\nickel{(A & B) | (A & C)}.

This straightforward solutions makes composing the Keil and Thiemann
system with other existing systems more difficult; in the words
of Williams, Morris, and Wadler (see Section~\ref{sec:will-morr-wadl}):
``(\ldots) the monitoring semantics for contracts of intersection and union types given by Keil
and Thiemann are not uniform. (\ldots) If uniformity helps composition, then
special cases can hinder composition.''\cite{RootCauseOfBlame}
\info{(Yann) Does
it also make it less efficient? If $(A \& B)$ fails because of $B$, their
development causes to recheck the contract $A$ that has been duplicated?}
And it also could harm performance, or at least complicate an implementation,
since some sharing mechanism should be used to avoid checking the same contract,
over the same value, multiple times.\unsure{Arnaud says: this whole
  section is too abstract give concrete code and explain what goes
  wrong. It's fine to give code in Nickel syntax}

@@

\subsection{Williams, Morris, and Wadler}
\label{sec:will-morr-wadl}
\unsure{Subsection title?}

@@

\subsection{Racket}
\label{sec:racket}

\unsure{Todo}
